---
title: "Codebook"
author: "yisong"
date: "July 25, 2015"
output: 
  html_document: 
    keep_md: yes
---

This is the codebook for the tidy dataset created by run_analysis.R.

| Variables | Description |
| --------- |:-----------:|
| subject | ID of the subject whose activity has been recorded |
| activity | Activity name |
| fDomain | feature: Time domain signal or Frequency domain signal (Time of Freq) |
| fDevice | feature: Measuring device (Accelerometer of Gyroscope) |
| fAcceleration | feature: Acceleration signal (Body or Gravity) |
| fVariable | feature: (Mean or SD) |
| fJerk | feature: Jerk signal |
| fMagnitude | feature: Magnitude of the signal |
| fAxis | feature: signal in X, Y and Z directions (X, Y or Z) |
| count | number of datapoints used to compute variable average |
| average | Average of each variable for each activity and each subject |

Dataset structure
```{r}
str(dtTidy)
```

Key variables of the data table
```{r}
key(dtTidy)
```

Summary fo variables
```{r}
summary(dtTidy)
```

All combinations of features
```{r}
dtTidy[, .N, by=c(names(dtTidy)[grep("^f", names(dtTidy))])]
```


